\section{SYSTEM REQUIREMENTS}

\subsection{\underline{User Interface}}
\begin{itemize}
    \item The current iteration of the user interface operates via a top-level Command Line Interface (CLI) menu, presenting options for Steam games, local directory games, and an exit function.
    \item The next iteration of the user interface is currently in development for a more modular and interactive experience.
    \item System shall display main menu with launcher modes.
    \item System shall display discovered games with index, title, and identifier/path.
    \item System shall allow user to select and launch game by input.
    \item System shall provide clear feedback for invalid input and launch failures.
    \item System shall display recommendation list with score in ranked order (when ML module invoked).
\end{itemize}

\subsection{\underline{Software Interface}}
\begin{itemize}

\item \textbf{C++ Core Modules}
    \begin{itemize}
	\item \texttt{game\_manager}: local directory scan, sorting, launch.
	\item \texttt{store\_manager}: Steam registry detection, library parsing, Steam launch.
    \end{itemize}

\item \textbf{Python Module}
    \begin{itemize}
	\item Metadata ingestion from IGDB.
	\item Feature extraction and score calculation.
    \end{itemize}

\item \textbf{Planned UI Layer}
    \begin{itemize}
	\item Qt/QML frontend over C++ backend services.
    \end{itemize}

\end{itemize}

\subsection{\underline{Database Interface}}
\begin{itemize}
    \item \textbf{Game catalog records}: Comprehensive data on available titles and assets.
    \item \textbf{Session logs}: Tracking metrics such as start time, end time, and total playtime.
    \item \textbf{User preference flags}: Binary or categorical data (e.g., like/dislike) for personalization.
    \item \textbf{Mood-session records}: Links between specific user moods and their corresponding gameplay sessions.
    \item \textbf{Cached metadata references}: Localized pointers to external assets for optimized performance.
\end{itemize}

\subsection{\underline{Protocols}}
\begin{itemize}
    \item \textbf{Local Process Execution}: Utilizing \texttt{ShellExecute} on Windows for native system calls.
    \item \textbf{Steam Launch Protocol}: Integration of the \texttt{steam://run/<appid>} URI for direct game initialization.
    \item \textbf{IGDB API Integration}: Secure HTTPS communication using Twitch OAuth for metadata retrieval.
    \item \textbf{Inter-Language Bridge}: Internal C++ $\leftrightarrow$ Python data exchange via file-based JSON or an API bridge.
\end{itemize}
